Calorinator: an interactive floor game to maintain body fitness

### 2015-02-07 paper.tex
add pictures
add real picture at the end

    We wanted to provide a fitness application in order to perform common fitness exercises. Even in the contextual inquiry we got to know that a floor does not provide the necessary instruments to perform a rich and diverse workout. It lacks a possibility to train the shoulders for example. We tried to reduce the app to only a few possible training exercises, like push-ups, stepping and sit-ups. This would not improve the training behavior at all. We then created training exercises out of things one can do on a floor.

@@

@@

  Developing an interactive protoype for a floor requires a lot amount of work. Paper prototyping turned out to be a powerful tool in order to find flaws in our designs as users were able to imagine the system.

@@

>>>>

    We wanted to provide a fitness application in order to perform common fitness exercises. Even in the contextual inquiry we got to know that a floor does not provide the necessary instruments to perform a rich and diverse workout. It lacks a possibility to train the shoulders for example. We tried to reduce the application down to only a few possible training exercises, like push-ups, stepping and sit-ups. This would not improve the training behavior at all. We then created training exercises out of things one can do on a floor.

  \begin{figure}[htb]
    \centering
    \includegraphics[width=0.505\linewidth]{Image_18}
    \includegraphics[width=0.455\linewidth]{Image_19}
    \caption{A direct copy of the reality to a floor app does not improve anything}
    \label{fig:copy}
  \end{figure}

@@

  \begin{figure}[htb]
    \centering
    \includegraphics[width=0.32\linewidth]{Image_20}
    \includegraphics[width=0.53\linewidth]{Image_21}
    \caption{Direct, but unclear instructions can be replaced by game elements that let the user know what to do only by the game context}
    \label{fig:copy}
  \end{figure}

@@

  Developing an interactive prototype for a floor requires a lot amount of work. Paper prototyping turned out to be a powerful tool in order to find flaws in our designs as users were able to imagine the system.

@@

  \newpage

  \begin{figure}[htb]
    \centering
    \includegraphics[width=\linewidth]{Image_22}
    \caption{An image taken from a live Demo on the floor. The player is running in the forest territory and jumps over a fallen tree.}
    \label{fig:copy}
  \end{figure}
